\tool: Revisiting BadUSB with Type-C

### 2021-01-28 WOOT/Files/conclusion.tex
quick pass on discussion and conclusion.

>>>>

Leveraging the new features of USB 3.x~\cite{usb31,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The scripting mode largely extends the
original BadUSB and successfully bypasses existing defenses. The privacy
extraction mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The remote control mode
archives complete hijack of the target device, allowing us to perform various
type of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further tests its ability under different mode and proves it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtains and analyzes video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

As future work, we will further explore the potential of \textit{isolated UI
rendering} and implement it on a customized operating system. Moreover we also
hope to lower the power consumption for network transmission in \tool to make
it more practical.

### 2021-01-28 WOOT/Files/discussion.tex
quick pass on discussion and conclusion.

\subsection{Limitation}
There exist multiple limitations of \tool.
To begin with, \tool can only gain the information and control access of the host itself instead of external hardware.
Consequently, as we introduced in the Section\ref{sec:countermeasures}, \tool can hardly bypass the defence approaches which use external hardware for authorization.
Moreover, most of the devices will prompt users to give authentication to the USB devices or select one of the functional modes after they are plugged in.
Though some of such prompts are not conspicuous for non-experts, especially when \tool is concealed within other functional hardware such as power banks \shuqing{If there is experiment, add it here.}, the probability whether users could get aware that something unusual happens will increase with the existence these prompting messages.

\subsection{Impact}
%\shuqing{Left after experiment to finish. Will discuss from different modes and application scenarios.}
The USB protocol is used widely as introduced in preceding sections.
As the technologies develops rapidly, more and more devices will be equipped with USB-C capabilities, which makes \tool more influential.
Due to the neglection to check the security of plugged-in USB devices of non-professional users, \tool can be hardly detected by them while attacks are performing.
The popularity and universality of public USB devices, including sharing power banks, even increase such risks.
What's more, \tool provides a better way for traditional BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as interacting with user interface, as well as control the consequences of their attacks.
In summary, \tool can be applied in various application scenarios and brings rather huge impacts.

>>>>

\subsection{Limitation}

There exist multiple limitations of \tool.  To begin with, \tool can only gain
the information and control access of the host itself instead of external
hardware.  Consequently, as we introduced in the
Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
approaches which use external hardware for authorization.  Moreover, most of
the devices will prompt users to give authentication to the USB devices or
select one of the functional modes after they are plugged in.  Though some of
such prompts are not conspicuous for non-experts, especially when \tool is
concealed within other functional hardware such as power banks \shuqing{If
there is experiment, add it here.}, the probability whether users could get
aware that something unusual happens will increase with the existence these
prompting messages.

\subsection{Impact}

%\shuqing{Left after experiment to finish. Will discuss from different modes
%and application scenarios.}
The USB protocol is used widely as introduced in preceding sections.  As the
technologies develop rapidly, more and more devices will be equipped with USB-C
capabilities, which makes \tool more influential.  Due to the neglection to
check the security of plugged-in USB devices of non-professional users, \tool
can be hardly detected by them while attacks are performing.  The popularity
and universality of public USB devices, including sharing power banks, even
increase such risks.  Moreover, \tool provides a better way for traditional
BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as
interacting with user interface, as well as control the consequences of their
attacks.  In summary, \tool can be applied in various application scenarios and
brings rather huge impacts.
